\Large \bf On semidefinite-representable sets over valued fields

### 2025-06-10 article/paper_padic_spec.tex
commit by Simone

\subsection{Notation}

@@

\subsection{Real spectrahedra}

Let $\sym_d(\R) \subset \R^{d\times d}$ be the vector space of $d \times d$ real symmetric
matrices. A matrix $M \in \sym_d(\R)$
is called \emph{positive semidefinite} ($M \succeq 0$) whenever the quadratic
form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$. By the Spectral Theorem, $M \succeq 0$
if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors
of $M$ being nonnegative. The set of positive semidefinite matrices, denoted $\sym_d^+(\R) \subset \sym_d(\R)$,
is a closed convex cone with non-empty interior in $\sym_d(\R)$.

>>>>

@@

Let $\sym_d(\R) \subset \R^{d\times d}$ be the vector space of $d \times d$ real symmetric
matrices. A matrix $M \in \sym_d(\R)$ is \emph{positive semidefinite} ($M \succeq 0$) whenever the quadratic form $x \mapsto x^TMx$ is nonnegative for all $x\in \R^n$. By the Spectral Theorem, $M \succeq 0$ if and only if the eigenvalues of $M$ are nonnegative, and this is equivalent to all the principal minors of $M$ being nonnegative. The set $\sym_d^+(\R) \subset \sym_d(\R)$ of positive semidefinite matrices is a closed convex cone with non-empty interior in $\sym_d(\R)$.
